Efficient Management of Reified Statements in RDF

### 2012-06-07 trunk/paper-iswc-reification/mainext.tex
added a second version of the paper that is meant to become the extended version with an appendix that contains all proofs

%\sloppy
\title{Efficient Management of Reified Statements in RDF}

@@

\input{intro}
\input{related}
\input{dis}
\input{rep}
\input{querying}
\input{exp}
\input{conc}

%\begin{appendix}
%\input{appendix}
%\end{appendix}
%
\bibliographystyle{abbrv}
\bibliography{paper}
\end{document}

>>>>

%\sloppy
\title{Efficient Management of Reified Statements in RDF}
\subtitle{(Extended Version)\footnote{This report presents an extended version of a paper submitted to ISWC 2012. This extended version contains proofs for all
	%propositions, lemmas, and theorems
	technical results
in the paper (cf.~\appendixname~\ref{Appendix:Proofs}).}
% \vspace{-5mm} % Layout Adjustment
}

@@

\input{intro}
For full technical proofs of all propositions in this paper we refer to \appendixname~\ref{Appendix:Proofs}.

\input{related}
\input{dis}
\input{rep}
\input{querying}
\input{exp}
\input{conc}

%\begin{appendix}
%\input{appendix}
%\end{appendix}
%
\bibliographystyle{abbrv}
\bibliography{paper}

\newpage
\appendix
\input{proofs}

\end{document}
